---
title: "Lab 00 - Hello IDS!"
author: "Sahasra Vundavalli"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Alice", "Bob", "Charles", 
           "Dan", "Edith"),
  github_username = c("alice_01", "bob_02", "charles_03", 
                      "dan_0", "edith_05"), 
  colour = c("powderblue", "darkred", "beige", 
             "navy", "darkgreen"),
  hobby = c("Hopping", "Dancing", "Partying", 
            "Reading", "Singing"),
  favourite_number = c(1, 2, 3, 4, 5)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


The plot shows the members github usernames plotted against their favourite number with the bars for each person being the colour of their favourite colour.

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "github usernames", 
          y = "favourite number",
          title = "lab groups github names against their favourite numbers")
```

Labs adds labels to the axis and can add a title to the plot.

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

The axis for the count has decimal numbers which isn't appropriate cause a fraction of a person cannot have a certain hobby. This data could be represented better using a pictograph possibly.
